Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Metric

### 2019-01-13 ICML2019/main.tex
fix plot
working on the abstract

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
\input{macros}
\icmltitlerunning{Exploring Design Space for Differentially Private Bayesian Inference}

@@

\twocolumn[
\icmltitle{Exploring Design Space for Differentially Private Bayesian Inference}

@@

\begin{icmlauthorlist}
\icmlauthor{Jiawen Liu}{to}
\icmlauthor{Mark Bun}{ed}
\icmlauthor{Gian Pietro Farina}{to}
\icmlauthor{Marco Gaboardi}{to}
\end{icmlauthorlist}

@@

\begin{abstract}
% Several approaches have been explored in order to make Bayesian inference
% differentially private.
% For instance, \cite{dimitrakakis2014robust} and
% \cite{wang2015privacy} proved that, under specific conditions of the likelihood function and the prior distribution,
% sampling from the posterior distribution, is already differentially private. \cite{zhang2016differential} and \cite{foulds2016theory}
% designed differentially private (d.p.) mechanisms by adding laplacian noise
% to the numeric parameters of the posterior distributions. 
% Accuracy, is usally (\cite{??}) measured by providing upper bounds, holding w.h.p, on the
% $\ell_1$ or $\ell_\infty$-distance between the numeric parameters
% of the released posterior distribution and the actual real ones of posterior distribution.
We explore the design space for differentially private Bayesian
inference.  We focused on two discrete models for parametric Bayesian
inference i.e., the Beta-Binomial and the Dirichlet-multinomial
models. We propose a variation of the exponential mechanism that uses
a scoring function based on a metric over probailistic measures, i.e.,
the Hellinger distance. We compare it with other approaches based on
the perturbation of the parameters of the posterior distribution.  We
measure the accuracy using the Hellinger distance over the posterior
distribution released and the real one as opposed to measuring the
$\ell_1$ or $\ell_{\infty}$ distance on the parameters.  We finally
present an experimental analysis on the accuracy of these mechanisms.
\end{abstract}
 % TODO: replace with your keywords

>>>>

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
\input{macros}
\icmltitlerunning{Exploring the Design Space of Differentially Private
  Bayesian Inference under Hellinger Metric}

@@

\twocolumn[
\icmltitle{Exploring the Design Space of Differentially Private
  Bayesian Inference under Hellinger Metric}

@@

\begin{icmlauthorlist}
\icmlauthor{Jiawen Liu}{to}
\icmlauthor{Gian Pietro Farina}{to}
\icmlauthor{Mark Bun}{ed}
\icmlauthor{Marco Gaboardi}{to}
\end{icmlauthorlist}

@@

\begin{abstract}
% Several approaches have been explored in order to make Bayesian inference
% differentially private.
% For instance, \cite{dimitrakakis2014robust} and
% \cite{wang2015privacy} proved that, under specific conditions of the likelihood function and the prior distribution,
% sampling from the posterior distribution, is already differentially private. \cite{zhang2016differential} and \cite{foulds2016theory}
% designed differentially private (d.p.) mechanisms by adding laplacian noise
% to the numeric parameters of the posterior distributions. 
% Accuracy, is usally (\cite{??}) measured by providing upper bounds, holding w.h.p, on the
% $\ell_1$ or $\ell_\infty$-distance between the numeric parameters
% of the released posterior distribution and the actual real ones of posterior distribution.
We explore the design space of differentially private Bayesian
inference mechanism.  We focus on two discrete models for parametric Bayesian
inference: the Beta-Binomial and the Dirichlet-multinomial
models. We propose a variation of the exponential mechanism that uses
a scoring function based on a metric over probailistic measures, i.e.,
the Hellinger distance. We compare it with other approaches based on
the perturbation of the parameters of the posterior distribution.  We
measure the accuracy using the Hellinger distance over the posterior
distribution released and the real one as opposed to measuring the
$\ell_1$ or $\ell_{\infty}$ distance on the parameters.  We finally
present an experimental analysis on the accuracy of these mechanisms.
\end{abstract}
 % TODO: replace with your keywords
